---
title: "Example image processing workflow (VIGNETTE UNDER DEVELOPMENT)"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example image processing workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Load required packages

```{r setup, message=FALSE}
library(EBImage)
library(dplyr)
library(SlakeItEasy)
```

## Interactively set paths to images and output directory 

```{r, eval=FALSE}
paths <- set_paths(parent_dir_img = system.file("images/", package="SlakeItEasy"), batch_name = 'example_output')
```

(Manually create `paths` list for vignette.)
```{r}
paths <- list(image_dir = 'images', batch_name = 'example_output', output_dir = 'tmp/example_output')
```

## Create directory for output

subdirectories for problematic images 

```{r}
dirs_for_flagged_imgs <- dir_setup(paths$output_dir,  return_paths = T)
```

## Extract metadata for images 

```{r}
metadata <- get_metadata(paths$image_dir, filename_prefix = 'IMG_')
```

## Check for replicates that do not meet expectations for analysis

```{r}
metadata_qaqc <- check_replicates(metadata,  final_img_time_min = 10, final_img_tol_sec = 30, n_images_max = 3)

write.csv(metadata_qaqc$m, paste0(paths$output_dir, '/qaqc_log.csv'), row.names = F)

metadata_qaqc$usable
metadata_qaqc$missing_imgs
metadata_qaqc$extra_imgs
metadata_qaqc$multiple_sizes
metadata_qaqc$wrong_final_time

# metadata[metadata$Directory %in% metadata_qaqc$wrong_final_time,]

# usable with resizing -- to processes these, set match_resolution = T in batch_process
to_analyze <- metadata_qaqc$multiple_sizes[!metadata_qaqc$multiple_sizes %in% c(metadata_qaqc$missing_imgs, metadata_qaqc$wrong_final_time, metadata_qaqc$extra_imgs)]

# full set of usable images
to_analyze <- c(metadata_qaqc$usable, to_analyze)

# inspect replicates with extra images
if (length(metadata_qaqc$extra_imgs) > 0) {
  opendirs(metadata_qaqc$extra_imgs)
}
```

## Process individual images

The suitability of default function arguments and need for alternative values can be evaluated by running `mask_image_circular()` and/or `area_from_image()`. If the sample container (Petri dish) is off-center in the image, modify the mask offsets (`h_offset` and `v_offset`). If the mask needs to be resized, modify the relative diameter of the mask (`d`).

```{r, eval = F}
img <- read_to_portrait(with(metadata[1,], paste0(Directory, '/', FileName)))
img_masked <- mask_image_circular(img, interactive = T, h_offset = 0)
plot(img_masked)

test <- area_from_image(with(metadata[1,], paste0(Directory, '/', FileName)), circular_mask = T, d = 0.73, interactive = T)
```

## Automated batch processing with a circular crop 

```{r}
results <- batch_process(dir_vec = to_analyze, outdir = paths$output_dir, filename_prefix = 'IMG_', match_resolution = T, circular_mask = T, parallel = T)
```

## Inspect classifications and sort suboptimal images 

```{r, eval = F}
reprocess_dir <- dirs_for_flagged_imgs['to_reprocess']
unusable_dir <- dirs_for_flagged_imgs['unusable']
opendirs(c(unusable_dir, reprocess_dir, paste0(paths$output_dir, '/images_false_color')))
```

## Prepare for manual processing 

```{r, eval = F}
images_to_reprocess <- list.files(reprocess_dir)

dir_vec2 <- unique(sapply(strsplit(images_to_reprocess, '_x_'), function(x) paste(x[1:(length(x) - 1)], collapse = '/')))
```


## Process images requiring manual crop 

```{r, eval = F}
results2 <- lapply(dir_vec2, function(i) {
  print(paste0('Processing ', i, '...'))

  out <- data.frame(image_set = i, stab10 = process_petri(i, interactive = T, match_resolution = T, circular_mask = T, filename_prefix = 'IMG_', outdir = paths$output_dir, aggregates_in_initial = 3))
  return(out)
}
) %>% bind_rows()
```

## Clean up

```{r, eval = F}
opendirs(c(unusable_dir, reprocess_dir, paste0(paths$output_dir, '/images_false_color')))
```

## Get IDs of unusable images

```{r, eval = F}
unusable <- gsub('.jpg', '', list.files(unusable_dir))
unusable <- unique(sapply(strsplit(unusable, '_x_'), function(x) paste(x[length(x) - 1])))
```

## Concatenate automatically & manually processed data 

```{r}
if (exists('results2')) {
 if (nrow(results2) > 0) {
  results <- bind_rows(results, results2)
}
}

results <- results %>%
  mutate(replicate_id = sapply(strsplit(image_set, '/'), function(x) x[[length(x)]]),
         replicate_num = substr(replicate_id, nchar(replicate_id), nchar(replicate_id)),
         sample_id = sapply(strsplit(replicate_id, '_'), function(x) x[[1]])) 

if (exists('unusable')) {
results <- results %>%
  filter(!replicate_id %in% unusable)
}
```

## Save results to disk

```{r}
results %>%
  write.csv(paste0(paths$output_dir, '/', paths$batch_name, '_stab10_results.csv'), row.names = F)
```

## Summarize results by sample

```{r}
results %>%
  group_by(sample_id) %>%
  summarise(stab10_mg = mean_geom(stab10), stab10_cv = cv(stab10), nreps = n())
```







